Manuscript_Github_Pchabaudi_compBerghei

### 2022-08-26 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_compBerghei.Rmd
Alter plots of berg comparison subfam proportions so that the graphs have same font size between each and don't show gene stacks

```{r chab_subfam_normByGeneNum}
chab_tpm_subfam.df.long <- chab_tpm.df %>% 
  rownames_to_column('Geneid') %>% 
  filter(Geneid %in% cir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(subfam = cir_info$subfam_num[match(Geneid, cir_info$Geneid)],
         SorL = cir_info$SorL[match(Geneid, cir_info$Geneid)],
         transmission = str_extract(sample, pattern = 'rMT|SBP'),
         time = str_extract(sample, '[[:digit:]]{2}h|sch.culture'),
         name = paste0(time, str_extract(sample, 
                                         pattern = '(_[[:digit:]]$)')))

@@

```{r berghei_subfam}
berg_tpm_subfam.df.long <- berghei_tpm[,
                                       c('Geneid',
                                         str_subset(colnames(berghei_tpm), 
                                                    pattern = 'Asex\\.(?!Mixed)'))] %>% 
  filter(Geneid %in% bir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(subfam = bir_clade$subfam_num[match(Geneid, bir_clade$Geneid)],
         experiment = str_extract(sample, pattern = '^E[[:digit:]]{2}'),
         stage = str_extract(sample, 'Asex.+(?=_[[:digit:]])'),
         name = str_extract(sample, '(?<=Asex\\.).+'))

( plot <- ggplot(filter(berg_tpm_subfam.df.long, subfam != 'ancestral (n = 1)'), 
                 aes(x = factor(name,
                                levels = ordering(name,
                                                  order_vector = c('Ring','Troph','Schiz','Mixed'))),
                     y = tpm,
                     fill = subfam)) +
    geom_col(position = "fill") +
    ylab("TPM") +
    xlab('stages') +
    scale_fill_manual(values = bir_clade_col_num[!grepl(names(bir_clade_col_num), 
                                                        pattern =  'ancestral')]) +
    facet_wrap(~experiment, scales = "free_x")+
    theme_classic()+
    theme(axis.text.x = element_text(angle = 90)) )

if(global_save_var){
  ggsave(plot,
         file = 'plots/berghei_subfamProp_AsexExact.png',
         width = 7,
         height = 9,
         units = "in")
}
```

>>>>

```{r chab_subfam_normByGeneNum}
chab_tpm_subfam.df.long <- chab_tpm.df %>% 
  # rownames_to_column('Geneid') %>% 
  filter(Geneid %in% cir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(subfam = cir_info$subfam_num[match(Geneid, cir_info$Geneid)],
         SorL = cir_info$SorL[match(Geneid, cir_info$Geneid)],
         transmission = str_extract(sample, pattern = 'rMT|SBP'),
         time = str_extract(sample, '[[:digit:]]{2}h|sch.culture'),
         name = paste0(time, str_extract(sample, 
                                         pattern = '(_[[:digit:]]$)'))) %>% 
  group_by(subfam, SorL, transmission, time, name) %>% summarise(tpm = sum(tpm))

@@

```{r berghei_subfam}
berg_tpm_subfam.df.long <- berghei_tpm[,
                                       c('Geneid',
                                         str_subset(colnames(berghei_tpm), 
                                                    pattern = 'Asex\\.(?!Mixed)'))] %>% 
  filter(Geneid %in% bir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(subfam = bir_clade$subfam_num[match(Geneid, bir_clade$Geneid)],
         experiment = str_extract(sample, pattern = '^E[[:digit:]]{2}'),
         stage = str_extract(sample, 'Asex.+(?=_[[:digit:]])'),
         name = str_extract(sample, '(?<=Asex\\.).+')) %>% 
  group_by(subfam, experiment, stage, name) %>% summarise(tpm = sum(tpm))

( plot <- ggplot(filter(berg_tpm_subfam.df.long, subfam != 'ancestral (n = 1)'), 
                 aes(x = factor(name,
                                levels = ordering(name,
                                                  order_vector = c('Ring','Troph','Schiz','Mixed'))),
                     y = tpm,
                     fill = subfam)) +
    geom_col(position = "fill") +
    ylab("TPM") +
    xlab('Stages') +
    scale_fill_manual(values = bir_clade_col_num[!grepl(names(bir_clade_col_num), 
                                                        pattern =  'ancestral')]) +
    facet_wrap(~experiment, scales = "free_x")+
    theme_classic()+
    theme(axis.text.x = element_text(angle = 90,
                                     hjust = 1),
          strip.text = element_text(size = 12),
          axis.text.y = element_text(size = 10),
          axis.title = element_text(size = 12))
)

if(global_save_var){
  ggsave(plot,
         file = 'plots/berghei_subfamProp_AsexExact.png',
         width = 7,
         height = 8,
         units = "in")
}
```
